Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-08-07 paper/paper.tex
Address
Write a tiny bit

\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{tikz}

@@

@@

\author{Samba Ndojh Ndiaye}
\affiliation{
    \institution{Universit\'e Lyon 1, LIRIS, UMR5205}
    \postcode{F-69621, France}
}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
\end{CCSXML}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}

% \keywords{ACM proceedings, \LaTeX, text tagging}

@@

@@

\subsection{A Basic Constraint Model}

\subsection{Ensuring Connectedness}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{dblp}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{tikz}

@@

\newcommand{\citepos}[1]{\citet{#1}'s}

@@

\author{Samba Ndojh Ndiaye}
\affiliation{
    \institution{Universit\'e Lyon 1, LIRIS, UMR5205}
    \city{F-69621, France}
}

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003809.10003716.10011136</concept_id>
<concept_desc>Theory of computation~Discrete optimization</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003809.10010170</concept_id>
<concept_desc>Theory of computation~Parallel algorithms</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003809.10011254.10011256</concept_id>
<concept_desc>Theory of computation~Branch-and-bound</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003790.10003795</concept_id>
<concept_desc>Theory of computation~Constraint and logic programming</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Discrete optimization}
\ccsdesc[500]{Theory of computation~Parallel algorithms}
\ccsdesc[500]{Theory of computation~Branch-and-bound}
\ccsdesc[300]{Theory of computation~Constraint and logic programming}

\keywords{Maximum common subgraph, Parallel branch and bound, Constraint programming}

@@

?? Explain induced, give examples.

Finding a maximum common subgraph is the key step in measuring the similarity or difference between
two graphs \citep{DBLP:journals/prl/Bunke97,DBLP:journals/prl/FernandezV01,o:Kriege15}: to determine
the difference between two graphs, we find what they have in common, and then take everything left
over. Because of this, maximum common subgraph problems frequently arise in biology and chemistry
\citep{DBLP:journals/jcamd/RaymondW02a,o:EhrlichR11,DBLP:journals/dam/GayFMSS14} where graphs
represent molecules, but also in applications including computer vision
\citep{DBLP:journals/jair/CookH94,DBLP:conf/gbrpr/CombierDS13}, computer-aided manufacturing
\citep{o:LuoWSN17}, crisis management \citep{o:DelavalladeFLL16}, deanonymising datasets
\citep{o:SharadD13}, the analysis of source code \citep{DBLP:journals/tkde/DjokoCH97}, binary
programs \citep{DBLP:conf/icics/GaoRS08}, and circuit designs \citep{DBLP:journals/jair/CookH94}, in
malware detection \citep{DBLP:journals/compsec/ParkRS13}, social network analysis
\citep{DBLP:journals/tkde/FangYZZ15}, graph database query explanations
\citep{DBLP:journals/jcss/VasilyevaTBL16}, and in character recognition problems
\citep{DBLP:journals/pr/LuRS91}.

?? Connected, which occurs in many applications
\citep{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,o:EhrlichR11,o:LuoWSN17}.
Adding the connectedness requirement makes certain special cases solvable in polynomial time,
including outerplanar graphs of bounded degree \citep{DBLP:journals/algorithms/AkutsuT13} and trees
\citep{DBLP:conf/mfcs/DroschinskyKM16}, but the general case remains \NP-hard. As illustrated in
\cref{figure:mcsexample}, the maximum common connected subgraph cannot be deduced from the maximum
common subgraph.

This paper looks at three recent branch and bound algorithms, each of which is the state of the art
for certain classes of instance.

The ultimate aim of this chapter is to parallelise a state-of-the-art algorithm for maximum common
subgraph problems, and to see whether we agree with \citepos{DBLP:conf/ictai/MinotNS15} conclusion
that doing so is unusually challenging.

@@

The maximum common subgraph problem may be reformulated as a constraint optimisation problem, as
follows. We pick whichever input graph has fewer vertices, and call it the \emph{pattern}; the other
graph is called the \emph{target}. The model is then to construct an injective, partial mapping from
the pattern to the target, preserving both adjacency and non-adjacency. Thus, for each
vertex in the pattern, we create a variable, whose domain ranges over each vertex in the target
graph, plus an additional value $\bot$. We then have three sets of constraints. The first set says
that for each pair of adjacent vertices in the pattern (that is, for each edge in the pattern),
if neither of these vertices are mapped to $\bot$ then these vertices must be mapped to an adjacent
pair of target vertices. The second set is similar, but looks at non-adjacent pairs (or non-edges).
Finally, the third set ensures injectivity, by enforcing that the variables must be all different
except when using $\bot$.

?? Either by binary constraints between all pairs, or a specialised propagator.

?? Objective.

?? One approach is branch and bound search over this model. Pick a variable, ... . cite.

?? Ensuring connectedness

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{combined}
